---
title: "Iteration and List Columns"
author: "Emma Sexton"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

```{r}
vec_numeric <- 5:8
vec_logical <- c(TRUE, FALSE, TRUE, TRUE)
```

Lets look at a list

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items

```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


## Loops!

Let's write a `for` loop to take the mean nand SD of four samples from a normal distribution

```{r}
list_norm = 
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, 0.4),
    d = rnorm(20, 100, 1)
  )


```

Here's my function

```{r}
mean_and_sd <- function(x) {
  
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
   }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Let's try to make this work.

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's try a `for` loop instead.

```{r}
output = vector("list", length = 4)
# this is an empty list -- this is where we're going to put the output

output[[1]] = mean_and_sd(list_norm[[1]])
# now we want to do that multiple times

for(i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])

}

output
```

## Can we map??

We can map!!

```{r}
map(list_norm, mean_and_sd)
```

So... what about other functions?

```{r}
map(list_norm, median)
map(list_norm, var)
map(list_norm, summary)
```

map variants...

```{r}
map(list_norm, median)
# sometimes lists are a hassle

map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)
# these simplify the outputs

output = map_df(list_norm, mean_and_sd)
# can also save it as above^
```

## List columns...

```{r}
listcol_df =
  tibble(
    name = c("a", "b", "c", "d"),
    norm = list_norm
  )

listcol_df[["norm"]]

map(listcol_df[["norm"]], mean_and_sd)
# only thing change is that now that's in a data frame, extract variable, then apply function
# problem: output isn't in the data frame
```

Can we add list columns, and then what

```{r}
listcol_df %>% 
  mutate(
    m_sd = map(norm, mean_and_sd)
  ) %>% 
  select(-norm)
```

## What about something more realistic...

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's nest within weather stations...

```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
# collapse down to a single data frame
```

Really is a list column!

```{r}
weather_nest_df[["data"]]
```

```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[3]])
# for a different data set each time (Waikiki, Central Park, and Waterhole)
```

Let's write a short lil ol function

```{r}
weather_lm = function(df) {
  
  lm(tmax ~ tmin, data = df)
  
}

weather_lm(weather_nest_df[["data"]][[1]])
```

Advantage of having a function is we can map across a list of data frames

```{r}
map(weather_nest_df[["data"]], weather_lm)
```

Spits out a LIST with a linear model of each thing

Map function -- give it an input LIST and a FUNCTION; it'll apply that element to each element of that list (which can be a data frame -- see nested)

One more problem to solve... we have to pull out the data frame

Start with data frame and mutate to add a column that is a list of linear regression results

Can I do all this in a tidy way?

```{r}
weather_nest_df %>% 
  mutate(
    models = map(data, weather_lm)
  )
```

YUP


Unnesting

```{r}
weather_nest_df %>% 
  unnest(data)
# gets you back to the data column you had
```


## Napoleon!!

Here's my scraping function that works for a single page:

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

What we did last time:

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, 1:5)

map(vec_url, read_page_reviews)

napoleon_reviews = 
  tibble(
    page = 1:5,
    page_url = str_c(base_url, page)
  ) %>% 
  mutate(
    reviews = map(page_url, read_page_reviews)
  )

napoleon_reviews %>% 
  select(-page_url) %>% 
  unnest(reviews)
```


