---
title: "Simulation"
author: "Emma Sexton"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Notes from last class / in general

Edit and highlight multiple lines of text at one time: Shift + Option and select the number of lines

Might have to re-install git when you update your computer


## Simulations!!!

Here's our function from before:


```{r}
sim_mean_sd = function(n_obs, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n_obs, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

How did we use this before?

```{r}
sim_mean_sd(n_obs = 30)
```


How can we use this now...

Let's start with a `for` loop!

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(n_obs = 30)
  
}

bind_rows(output)
```


Let's use list columns instead...

```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iteration = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) +
  geom_density()
```


!!!!!!!!!!!!!!!!!!!

## What about changing the sample size?

I need an input list with lots of sample sizes

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iteration = 1:1000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin()
```


```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  group_by(sample_size) %>% 
  summarize(
    empt_st_err = sd(mu_hat)
  )
```


## Let's see two inputs ...

How to map over two inputs at one time

```{r, cache = TRUE}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    true_sigma = c(6, 3),
    iteration = 1:1000
  ) %>% 
  mutate(
    estimate_df = 
      map2(.x = sample_size, .y = true_sigma, ~ sim_mean_sd(n_obs = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)
```

^^ Naming inputs very explicitly in `estimate_df`; also HAVE to use .x and .y AND the ~ (tilda)


```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin() +
  facet_grid(. ~ true_sigma)
```


Be cautious about CACHE-ing results -- it'll save whatever is written in that code chunk, but it won't re-run unless you change something in that code chunk



